\thispagestyle{plain}

\newgeometry{left=3.67cm,right=3.17cm,top=2.54cm,bottom=2.54cm}

\begin{center}
%    \large
    
    {\fontfamily{ptm}\selectfont

    \textbf{Synote Testing Framework}\\
        
    \vspace{1cm}
    
    \textbf{Group 8} \\
	Shakib-Bin Hamid \\ Thomas Aley \\ Deepak Thankachan \\ Vlad Catrici    
    
    \vspace{2cm}
	}    
\end{center}


%\large
{\fontfamily{ptm}\selectfont
\textbf{Supervisor}: Professor Mike Wald\\
\textbf{2nd Examiner}: Dr Sepideh Chakaveh\\
\textbf{Customer}: Synote Limited (Professor Mike Wald and Dr Yunjia Li) 12 Merlin Way, Eastleigh, SO53 4JB
}

\vspace{1cm}

\begin{framed}

{\fontfamily{ptm}\selectfont
Abstract\\

Synote, a company derived from previous successful projects at the University of Southampton, provides automated transcripts for uploaded videos. However, it required a payment system. It was also ineffective in its previous efforts to build an End-to-End (E2E) testing framework and did not have a Continuous Integration (CI) process in place. All three are mission critical for any successful software company. Initially, GDP team 8 set out to deliver the former two. At the same time, they achieved $\approx$ 100\% test coverage in their implementation using unit, integration and E2E tests. Near the end, the team focused on implementing a CI process for Synote as an extension to the project. Overall the group delivered a secure payment system, a practical E2E testing framework with comprehensive tests and a CI implementation for the experiment stage of deployment. They also provided the E2E testing methodology and the QA process as a document. This report will cover the details of each of the deliverables, as well as the team management and future works of the project.
}
\end{framed}

\restoregeometry

\large

