\chapter{Conclusion}
\label{chap:conclusion}

\section{Goals achieved}
\label{sec:goals-achieved}
Over the course of this project, our goals and objectives kept on changing as we kept on meeting our milestones and defined new ones. If at the beginning we sat out to provide our customer with an E2E testing framework and a payment feature, at the end we managed to overachieve and impress our client with a well-rounded continuous integration strategy. A consistent work ethic aided in us in meeting our objectives by setting out clear tasks and operating in an AGILE fashion.

\section{Customer satisfaction}
\label{sec:customer-sastisfaction}
As can be seen in \textbf{Appendix \ref{appendix:client-sign-off}}, the client is satisfied by the work we have done. Apart from achieving what was expected of us and surpassing expectations, we believe a good part of our customer's contentment is due to the fact that we tried to communicate as much as possible with him, giving him updates on our work and requesting feedback and help when needed.

\section{Was the project challenging?}
\label{sec:was-the-project-challenging}
We believe the project was very challenging as we had a limited amount of time to get acquainted with many technologies and practices that were new to us. The workload was not mindless in the slightest and we were required to do extensive research in order to find the path towards a robust solution. Because of this element of unknown, we needed to organise ourselves very well to achieve our goals and put in a lot of hours every week. We faced challenges when mitigating other responsibilities such as coursework, job interviews and personal issues and also technical problems which we needed to overcome.

\section{Was the project fun?}
\label{sec:was-the-project-fun}
We really enjoyed this project from start to finish. We liked that it challenged us from the beginning and that we had to work hard to better ourselves. Learning and experimenting with new technologies kept our interests high and gave us an incentive make as much progress as possible. We appreciated each other's work and company as we pushed forward to get the project done. All in all, we believe it was a wonderful experience.
